% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Vineeth V S}
% \address used twice to have two lines of address
\address{2vineethvs@gmail.com}
\address{+91 9847109218}

 
\begin{resume}
 
\section{OBJECTIVE}
  To excel in my field through hard work, research, skills and perseverance. To serve my country and humankind with the best of my abilities.
 
\section{ACADEMIC \\ EDUCATION} {\sl Under Graduation}\hfill 2009-2013\\
% \sl will be bold italic in New Century Schoolbook (or
% any postscript font) and just slanted in
% Computer Modern (default) font
   Bachelor of Technology, Computer Science \\
   College of Engineering, Trivandrum expected April 2013\\
   GPA till date (Average): 7.2

   {\sl Junior College} \hfill 2007-2009\\
   CPHSS Kuttikkadu Kadakkal Kollam (PCM + CS)\\
   HSE Aggregate : 90.83\% 
   
   {\sl High School} \hfill 2007\\
   Govt VHSS Chingeli Kadakkal\\
   SSLC Aggregate : 86.05\% 

\section{PROFESSIONAL \\ EDUCATION}  {\sl Embedded Systems Design And Programming, Mc University}\hfill Summer, 2011
 \begin{itemize}  \itemsep -2pt %reduce space between items
   \item 
     Course involved designing and programming with field programmable\\ mixed signal microcontroller (CIP 8051).
   \end{itemize}



\section{COMPUTER \\ SKILLS} {\sl Languages:} C, C++, java, SQL\\
   {\sl Tools:}  gcc, gdb, Netbeans, Eclipse, GNU/Emacs, Gimp, Photoshop\\
   {\sl Operating Systems:} Different Linux Flavours, Windows XP\\
   {\sl Embedded Platforms:} Development using Silicon Labs CIP 8051\\
 
\section{PROJECTS} Linux Distribution Developer  \hfill Winter, 2010 
  
  {\sl  Leave Management System} \hfill      Mini Project S5, 2011      
   \begin{itemize}  \itemsep -2pt %reduce space between items
   \item 
     Project involve development of a java based application software which manages the leaves system in an educational institution or a company. 
   \end{itemize} 

  {\sl Malayalam Speech Recognition} \hfill      Final year project S8, 2013      
   \begin{itemize}  \itemsep -2pt %reduce space between items
   \item 
    Project involve development of a menu driven java application for a public place like bus stand, which recognises malayalam words with limited vocabulary

 \end{itemize}

    
  	
\section{EXTRA-\\CURRICULAR \\ ACTIVITIES}     
\begin{itemize}  \itemsep -2pt %reduce space between items        
\item    Active member of FSUG-TVM.
\item     Member of Executive Panel,Student's Chapter IET.
\item Event Co-ordinator of Python Primer in College Of Engineering ,Trivandrum conducted by  IET-CET
\item Event Co-ordinator of Silicon Labs Programme in College Of Engineering ,Trivandrum conducted by IET-CET
\end{itemize}

\section{PARTICIPATION}
\begin{itemize}  \itemsep -2pt %reduce space between items   
\item   Indian Science Congress, Delegate  \hfill Trivandrum 
\item   FOSSMEET, Delegate  \hfill NIT Calicut
\item   Dot-slash 2011 CET,Delegate     \hfill Trivandrum
\item   Various technical fests in kerala conducted by Technical Institutions
\end{itemize}


\section{HOBBIES}
	
        Reading \\ 
        Billiards \\ 
        Cricket.  \\ 
       
\section{PERSONAL DETAILS}
 {\bf Permanent address:} 		 \\
	Sreenilayam \\
	Marupuram, \\
	Kadakkal PO \\
	Kollam 691536 \\
	Kerala        \\    
	
\section{DATE OF BIRTH } 
	Sept 12, 1990 
 
\section{DECLARATION} 
	The information that i have provided is true to the best of my knowledge and belief. 	
	
\end{resume}
\end{document}
